 

### 2021-02-03 vertical-thermal-review.Rmd
rearrangement
#41

**Here we review how the biophysical environment and biological form and function vary across the vertical canopy gradient in forests.** 
We focus on five key themes (Fig. `r fig_schematic`):
(1) the biophysical environment;
(2) the leaf traits that most strongly influence leaf temperature and metabolism;
(3) resulting leaf temperature ($T_{leaf}$) and
(4) foliar metabolism, including stomatal conductance, photosynthesis, respiration, and volatile organic compound (VOC) production; and 
(5) resultant size-structuring of whole-tree and ecosystem function.
*We then consider the implications for modeling /  climate change responses.*

@@

@@

## Leaf temperature

@@

[Elsa: do we want a section about research opportunities using remote sensing or is that outside the scope of this review?] 
An increasing availability of airborne and spaceborne LiDAR remote sensing data offers a promising opportunity for mapping vertical thermal gradients and vegetation structure. [Drone based FLIR cams, tower thermal cams (Pau et al 2018), ECOSTRESS]. To evaluate large-scale ecosystem patterns, high resolution vertically resolved vegetation structure from LiDAR data can be analyzed in combination with collocated field measurements collected using towers (FluxNet REF), canopy cranes (@nakamuraForestsTheirCanopies2017), or by tree climbing (REF – e.g. Asner papers, Shenkin et al – Unding Jami’s work). Existing research efforts have already revealed incredibly heterogeneity in vegetation structure, diversity, traits, and properties both within and across ecosystems (REFS – Stovall, Schneider, …others).

## Implications

@@

@@

### Climate change responses

@@

>>>>

**Here we review how the biophysical environment and biological form and function vary across the vertical canopy gradient in forests.** 
We focus on five key themes (Fig. `r fig_schematic`):
(1) the biophysical environment;
(3) leaf hydraulics and temperature ($T_{leaf}$);
(2) the leaf traits most strongly influence leaf temperature and metabolism;
(4) foliar metabolism, including stomatal conductance, photosynthesis, respiration, and volatile organic compound (VOC) production; and 
(5) size-structuring of whole-tree and ecosystem function.
*We then consider the implications for understanding forest responses to global change, including  modeling /  climate change responses.*

@@

## Leaf hydraulics and temperature

@@

@@

## Projecting in time and space

@@

### Remote sensing 
[Elsa: do we want a section about research opportunities using remote sensing or is that outside the scope of this review?] 
An increasing availability of airborne and spaceborne LiDAR remote sensing data offers a promising opportunity for mapping vertical thermal gradients and vegetation structure. [Drone based FLIR cams, tower thermal cams (Pau et al 2018), ECOSTRESS]. To evaluate large-scale ecosystem patterns, high resolution vertically resolved vegetation structure from LiDAR data can be analyzed in combination with collocated field measurements collected using towers (FluxNet REF), canopy cranes (@nakamuraForestsTheirCanopies2017), or by tree climbing (REF – e.g. Asner papers, Shenkin et al – Unding Jami’s work). Existing research efforts have already revealed incredibly heterogeneity in vegetation structure, diversity, traits, and properties both within and across ecosystems (REFS – Stovall, Schneider, …others).

@@

## Global change responses

### warming

@@

### canopy disturbance
